\chapter{Facilities Required for Proposed Work}
\section{Predictive Analytic Requirements}
Building a decision requirements model 
to specify business understanding at the very beginning 
of 
a predictive analytic project allows the creation of predictive analytic requirements that:\begin{enumerate} 
	\item Describe a clear target for the project.
The 
decisions that the predictive analytic will 
influence are specified. The decision requirements diagram links these decisions to the 
ultimate business metrics or objectives that will be impacted by the analytic
.
	
	\item Identif
y
the analytics to be developed.
Each 
piece of analytic knowledge can be 
described a
long with the information to be analyzed to produce 
it
.
	
	\item Is specific about which decisions are being influenced.
The decision requirements 
diagram shows w
hich part of the 
decision making is influenced, exactly, 
by each 
predictive analytic model being developed and what other factors influence that 
decision
-
making.
	
	\item Is specific about deployment.
The links for the decisions involved show w
hich 
organizations will be involved
, w
hich business processes will be impacted
and w
hich 
systems will have to be altered.

A complete set of requirements for a predictive analytic project 
should include other project 
details such as executive sponsor, timeline, resources, planned analytic approach
, 
etc. The 
d
ecision 
r
equirements 
m
ode
l allows the business 
problem being addressed by 
the project to be 
described more precisely
,
but it does not replace these other elements.
	
\end{enumerate}

\section{Software Requirements:}
\begin{enumerate}
\item Python 2.7
\item Python pip
\item Anaconda
\end{enumerate}

\section{Python Packages Dependencies}
\begin{enumerate}
\item Pandas
\item Sklearn
\end{enumerate}

