\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\bibliographystyle{ieeetr} 
\begin{thebibliography}{22}


\bibitem{} "OpenSCAD - News", Openscad.org, 2016. [Online]. Available: http://www.openscad.org/news.html\#20160714. [Accessed: 27- Jan- 2016].

\bibitem{} "OpenSCAD - The Programmers Solid 3D CAD Modeller", Openscad.org, 2016. [Online]. Available: http://www.openscad.org. [Accessed: 27- Jan- 2016].

\bibitem{} "openscad/openscad", GitHub, 2017. [Online]. Available: https://github.com/openscad/openscad/wiki/Project\%3A-Multi-threaded-geometry-rendering. [Accessed: 30- Jan- 2017].
\bibitem{} "OpenSCAD User Manual/WIP - Wikibooks, open books for an open world", En.wikibooks.org, 2016. [Online]. Available: https://en.wikibooks.org/wiki/OpenSCAD\_User\_Manual/WIP\#Customizer. [Accessed: 27- Jan- 2016].

\bibitem{} "openscad/openscad", GitHub, 2016. [Online]. Available: https://github.com/openscad/openscad. [Accessed: 27- Jan- 2016].

\bibitem{} "Doxygen: Main Page", Doxygen.org, 2016. [Online]. Available: http://www.doxygen.org. [Accessed: 27- Nov- 2016].

\bibitem{} "OpenSCAD", En.wikipedia.org, 2016. [Online]. Available: https://en.wikipedia.org/wiki/OpenSCAD. [Accessed: 27- Jan- 2016].

\bibitem{} "OpenSCAD", Openscad.org, 2017. [Online]. Available: http://www.openscad.org/. [Accessed: 16- Apr- 2017].

\bibitem{} "User Interface for Customizing Models", amarjeetkapoor1, 2016. [Online]. Available: https://amarjeetkapoor1.wordpress.com/2016/07/04/user-interface-for-customizing-models/. [Accessed: 27- Jan- 2016].


\bibitem{} "User:Amarjeet Singh Kapoor/GSoC2016/Project - BRL-CAD", Brlcad.org, 2016. [Online]. Available: http://brlcad.org/wiki/User:Amarjeet\_Singh\_Kapoor/GSoC2016/Project. [Accessed: 27- Nov- 2016].

\bibitem{} "User Interface for Customizing Models ( Part 3)", amarjeetkapoor1, 2016. [Online]. Available: https://amarjeetkapoor1.wordpress.com/2016/08/17/user-interface-for-customizing-models-part-3/. [Accessed: 27- Nov- 2016].

\bibitem{} "openscad/openscad", GitHub, 2016. [Online]. Available: https://github.com/openscad/openscad/wiki/Project\%3A-Form-based-script-parameterization. [Accessed: 27- Nov- 2016].

\bibitem{} "User Interface for Customizing Models ( Part 2)", amarjeetkapoor1, 2016. [Online]. Available: https://amarjeetkapoor1.wordpress.com/2016/07/18/user-interface-for-customizing-models-part-2/. [Accessed: 27- Nov- 2016].

\bibitem{} "Qt (software)", En.wikipedia.org, 2016. [Online]. Available: https://en.wikipedia.org/wiki/Qt\_(software)\#/media/File:Qt\_logo\_2015.svg. [Accessed: 27- Nov- 2016].


\bibitem{} "",Upload.wikimedia.org, 2016. [Online]. Available: 

https://upload.wikimedia.org/wikipedia/commons/c/ce/Doxygen.png. [Accessed: 27- Nov- 2016].


\bibitem{} "Git", En.wikipedia.org, 2016. [Online]. Available: 

https://en.wikipedia.org/wiki/Git\#/media/File:Git-logo.svg. [Accessed: 27- Nov- 2016].


\bibitem{}"Qt (software)", En.wikipedia.org, 2016. [Online]. Available: https://en.wikipedia.org/wiki/Qt\_(software). [Accessed: 27- Nov- 2016].

\bibitem{} "C++", En.wikipedia.org, 2016. [Online]. Available: https://en.wikipedia.org/wiki/C\%2B\%2B. [Accessed: 27- Nov- 2016].

\bibitem{}"Travis CI", En.wikipedia.org, 2016. [Online]. Available: https://en.wikipedia.org/wiki/Travis\_CI. [Accessed: 27- Nov- 2016].

\bibitem{} "CMake/Testing With CTest - KitwarePublic", Cmake.org, 2016. [Online]. Available: https://cmake.org/Wiki/CMake/Testing\_With\_CTest. [Accessed: 27- Nov- 2016].

\bibitem{} "", I-msdn.sec.s-msft.com, 2017. [Online]. Available: https://i-msdn.sec.s-msft.com/dynimg/IC251606.jpeg. [Accessed: 16- Apr- 2017].

 \bibitem{} "Lambda Expressions in C++", Msdn.microsoft.com, 2017. [Online]. Available: https://msdn.microsoft.com/en-us/library/dd293608.aspx. [Accessed: 16- Apr- 2017].

 \bibitem{} "Using Lambda Expressions for Shorter, More Readable C++ Code -- Visual Studio Magazine", Visual Studio Magazine, 2017. [Online]. Available: https://visualstudiomagazine.com/articles/2012/06/18/cplus-lambda-expressions.aspx. [Accessed: 15- Apr- 2017].

 \bibitem{} "Visitor pattern", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Visitor\_pattern. [Accessed: 17- Apr- 2017].

 \bibitem{} "Visitor pattern", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Visitor\_pattern\#/media/File:Visitor\_design\_pattern.svg. [Accessed: 15- Apr- 2017].

 \bibitem{} "Boost (C++ libraries)", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Boost\_(C\%2B\%2B\_libraries). [Accessed: 17- Apr- 2017].
 
 \bibitem{} "GNU", En.wikipedia.org, 2016. [Online]. Available: 
 
 https://en.wikipedia.org/wiki/GNU\#/media/File:Heckert\_GNU\_white.svg. [Accessed: 27- Nov- 2016].
 
 \bibitem{} "GitHub", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/GitHub. [Accessed: 15- Apr- 2017].

\bibitem{} "Layer 1", Upload.wikimedia.org, 2017. [Online]. Available: https://upload.wikimedia.org/wikipedia/commons/2/24/GitHub\_logo\_2013\_padded.svg. [Accessed: 16- Apr- 2017].
 
\bibitem{} "", Upload.wikimedia.org, 2017. [Online]. Available: https://upload.wikimedia.org/wikipedia/commons/c/cd/Boost.png. [Accessed: 17- Apr- 2017].

\bibitem{} "Flex (lexical analyser generator)", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Flex\_(lexical\_analyser\_generator). [Accessed: 22- Apr- 2017].

\bibitem{} "GNU bison", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/GNU\_bison. [Accessed: 17- Apr- 2017].

\bibitem{} "JSON logo", Upload.wikimedia.org, 2017. [Online]. Available: https://upload.wikimedia.org/wikipedia/commons/c/c9/JSON\_vector\_logo.svg. [Accessed: 18- Apr- 2017].

\bibitem{} "JSON", Json.org, 2017. [Online]. Available: http://www.json.org/. [Accessed: 22- Apr- 2017].

\bibitem{} "STL Function Objects (Functors)", Cs.stmarys.ca, 2017. [Online]. Available: http://cs.stmarys.ca/~porter/csc/ref/stl/function\_objects.html. [Accessed: 15- Apr- 2017].

\end{thebibliography}